---
title: "Lab 3"
author: "Amber Jacobson"
date: "October 2, 2017"
output: html_document
---

## Question 1 

The Cars93 dataset in the MASS package contains data from 93 cars on sale in the USA in 1993. Randomly select 40 cars as the training dataset and the remaining 53 cars as the test dataset. 

```{r}
library(MASS)
df <- Cars93
training <- sample(df$Model, 40)
test <- sample(df$Model, 53, replace = FALSE)
```

```{r}
training
test
```

### Question 1A 

Save both datasets as csv files. Find out the number of USA and non-USA cars in the training dataset. 


```{r}
write.csv(training, file="training.csv")
write.csv(test, file="test.csv")
```

```{r}
## Ask how to find the number of USA and non-USA cars in the training dataset. Is it similarto what we did in the first lab?
```


## Question 2

Assume that the probabilities of boy and girl births are 0.515 and 0.485, respectively. Use the sample() function to simulate 10 births and print out the result. How many boys and girls do you get out of 10 births? Then simulate 10,000 births. How many boys and girls do you get out of 10,000 births?

```{r}
births <- sample(c("boy", "girl"), size = 10, replace = TRUE, prob=c(.515, .485))
births
table(births)
```

For this sample, the amount of boy and girl births were split equally. Let's see what happens when we sample significantly more births. 


```{r}
manybirths <- sample(c("boy", "girl"), size = 10000, replace = TRUE, prob=c(.515, .485))
table(manybirths)
```

In this sample, we can see how the probability affects the outcome of the number of boys versus girls--there were about 300 more boys than girls. 



## Question 3 

Assume that the probabilities of boy and girl births are 0.515 and 0.485, respectively. What’s
the probability of having exactly 3 boys out of 10 births? What’s the probability of having 8 or more boys out of 10 births? Plot both the density function and cumulative probability function of the number of boy births out of 10.

**Density function**
```{r}
dbinom(3, size=10, prob=.515)

dbinom(8, size=10, prob=.515)
```

**Cumulative probability function**
```{r}
pbinom(3, size=10, prob=.515)

pbinom(8, size=10, prob=.515)
```


## Question 4

If cars arrive randomly at a traffic light at the rate of five every ten seconds. What the probability that exactly four cars arrive in the next ten seconds? What’s the probability that more than five cars arrive in the next ten seconds? Plot the density function of 0-20 cars arriving in the next ten seconds.

```{r}
dbinom(4, size=1:20, prob=.5)
```

```{r}
pbinom(5, size=1:20, prob=.5)
#Would I use lower.tail = FALSE here?
```

